
    \section{Achievements, honours and awards}
    \achievement{My first achievement}
    \achievement{My second achievement}

    \section{General Skills}
    \smallskip % additional skip because tag outlines use up space
    \tag{Tag 1}
    \tag{Tag 2}
    \tag{and}
    \tag{another tag}
    \tag{some more tags}
    \tag{yet another one}
    \tag{tags flow over}
    \tag{to the next line}
    \tag{if necessary}
    
    \medskip
    Tags must be ordered by hand with newlines to get a nice layout, especially for long tags.
    
    \section{Wheel Chart}
    % This is taken from AltaCV
    % see https://github.com/liantze/AltaCV for details
    \wheelchart{1.5cm}{0.5cm}{% outer and inner diameter
        6/8em/accent!20/Sleep,          % comma-separated list of
        8/8em/accent!40/Daytime job,    % fraction of 24 / line length / color / label
        2/8em/accent!80/Training,          % here, the color is shades of the accent color
        3/8em/accent!60/Recovering from fighting criminals,
        5/8em/accent/Being Batman
    }

\makebody
\clearpage


\pagestyle{highlightmain}

% The highlightbar needs to be filled to display mainbar contents correctly in singlesised mode
% For an empty highlightbar, fill with empty space
\highlightbar{\hfill}
\mainbar{

    \section{Another section}
    
    This page uses the page style \texttt{highlightmain} which shows the highlight bar (gray) and the main part (white background) but omits the header. 
    The default page style is \texttt{headerhighlightmain} with all three elements.
    If you don't want header, nor highlight bar, use page style \texttt{\textbackslash pagestyle\{empty\}}.
    \medskip
    Neither main, nor highlight bar must be filled to make this template work.
    It is possible to use a page style with the highlight bar but leave it empty by setting an empty highlightbar \texttt{\textbackslash highlightbar\{\}}.

    \vspace{0.5em}
    \subsection{Subsection 1}
    Demonstrate subsections.
    
    \subsection{Subsection 2}
    Subsection are also bold face but a smaller font then section. They also omit the rule.
    

}
\makebody


\clearpage
\pagestyle{empty}

\section{Publications}
\pubforcefullwidth

Demonstrate what an \texttt{\textbackslash pagestyle\{empty\}} page looks like.
Also show off the macros for publications that uses small icons for authors, date, journal and links.

Achieving a good looking spacing can be tricky. For empty pagestyles where the full width is available use \texttt{\textbackslash pubforcefullwidth} to force the publoication list to take up all the available space.
The (relative) lengths reserved for date, journal and links can be set with the parameters \texttt{\textbackslash pubdatelength}, \texttt{\textbackslash pubjournallength} and \texttt{\textbackslash publinklength} as in \texttt{\textbackslash setlength\{\textbackslash pubdatelength\}\{0.15 \textbackslash linewidth\}}.
\bigskip

\publication
	{The turbulent gas structure in the centers of NGC~253 and the Milky Way} % Title
	{\textbf{N. Krieger}, A. Bolatto, E. Koch, A. Leroy, E. Rosolowsky, F. Walter, A. Wei\ss, D. Eden, R. Levy, D. Meier, E. Mills, T. Moore, J. Ott, Y. Su, S. Veilleux} % Authors
	{2020} % Year
	{The Astrophysical Journal Vol. 899, Issue 2, id.158} % Journal
	{\ADS{https://ui.adsabs.harvard.edu/abs/2020ApJ...899..158K}, \arXiv{https://arxiv.org/abs/2008.02518}} % ADS & arxiv links

\publication
	{The molecular ISM in the Super Star Clusters of the starburst NGC253} % Title
	{\textbf{N. Krieger}, A. Bolatto, A. Leroy, R. Levy, E. Mills, D. Meier, S. Veilleux, F. Walter, A. Wei\ss} % Authors
	{2020} % Year
	{The Astrophysical Journal Vol.897, Issue 2, id.176} % Journal
	{\ADS{https://ui.adsabs.harvard.edu/abs/2020ApJ...897..176K}, \arXiv{https://arxiv.org/abs/2006.08262}} % ADS & arxiv links

\publication
	{The Molecular Outflow in NGC\,253 at a Resolution of Two Parsecs} % Title
	{\textbf{N. Krieger}, A. Bolatto, F. Walter, A. Leroy, L. Zschaechner, D. Meier, J. Ott, A. Wei\ss, E. Mills, S. Veilleux, M. Gorski} % Authors
	{2019} % Year
	{The Astrophysical Journal Vol.881, Issue 1, article id. 43, 20 pp} % Journal
	{\ADS{https://ui.adsabs.harvard.edu/abs/2019ApJ...881...43K}, \arXiv{https://arxiv.org/abs/1907.00731}} % ADS & arxiv links
